---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(brac)
```
# About this package:

The package is about getting data from binance api with different functions.

1. **pingToServer()**

The function returns data frame of empty data just to confirm ping is working.

2. **checkServerTime()**

The function returns data frame of current server time.

3. **fetchSymbolOrderBook()**

The function returns the symbol order book.

4. **fetchSymbolTrades()**

The function returns symbol trades data frame.

5. **fetchSymbolAggTrades()**

The function returns the symbol aggregate trades data frame.

6. **fetchSymbolAveragePrice()**

The function returns the symbol average price data frame.

7. **fetchTicker24hPrice()**

The function returns the ticker 24h price data frame.

8. **fetchTickerPrice()**

The function returns the ticker price data frame.


